Gas Fractions of Galaxies Across Simulations

### 2018-07-12 mnras_template.tex

\begin{figure}
\includegraphics[width = 0.99\linewidth]{fgas_mstar_binned_IQR_logged.png}\\
\includegraphics[width = 0.99\linewidth]{gasless_fraction_mstar.png}
\caption{{\bf Top:} The running median of f$_{\rm gas}$ as a function of stellar mass for each dataset with shading denoting the inner quartile range of each. Unlike in Figure~\ref{fig:fgas mstar 2D}, this includes galaxies with zero neutral gas mass. {\bf Bottom:} The fraction of galaxies per stellar mass bin for each dataset that do not contain any neutral gas. The percent of all galaxies without gas in each dataset is shown in the legend.}
\label{fig:linear fgas mstar}
\end{figure}

@@

>>>>

\begin{figure*}
\includegraphics[width = 0.33\linewidth]{fgas_mstar_binned_IQR_logged.png}\\
\includegraphics[width = 0.33\linewidth]{MHI_Mstar_binned_IQR.png}
\includegraphics[width = 0.33\linewidth]{gasless_fraction_mstar.png}
\caption{{\bf Left:} The running median of f$_{\rm gas}$ as a function of stellar mass for each dataset with shading denoting the inner quartile range of each. Unlike in Figure~\ref{fig:fgas mstar 2D}, this includes galaxies with zero neutral gas mass. {\bf Middle} The running median of gas mass as a function of stellar mass for each dataset with shading denoting the IQR. {\bf Right:} The fraction of galaxies per stellar mass bin for each dataset that do not contain any neutral gas. The percent of all galaxies without gas in each dataset is shown in the legend.}
\label{fig:linear fgas mstar}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width = 0.99\linewidth]{fgas_DSFMS_2dhist_count_log_fgas.png}\\
\caption{2D histogram of fraction of galaxies in a given gas fraction and distance from SFMS bin.}
\label{fig:fgas DSFMS panel}
\end{figure*}
